A Study of the Effectiveness of Usage Examples in REST API Documentation

### 2017-08-01 controlled_study/controlled_study.tex
DRY up
structurally complete, sans abstract / introduction / conclusion
all chapters added
first reasonably ok pass

%\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%\def\ps@IEEEtitlepagestyle{%
  %\def\@oddfoot{\mycopyrightnotice}%
  %\def\@evenfoot{}%
%}
%\def\mycopyrightnotice{%
  %{\footnotesize 978-1-5386-0443-4/17/\$31.00 ©2017 IEEE\hfill}% <--- Change here
  %\gdef\mycopyrightnotice{}% just in case
%}
%\begin{document}
%\title{A Study of the Effectiveness of Usage Examples in REST API Documentation}
\chapter{A Study of the Effectiveness of Usage Examples in REST API Documentation}

@@

Starting January 2017, the WordPress REST API V2 is no longer required to be installed as a separate plug-in since it is bundled with WordPress installation. According to the code repository, there are a total of 99 and 46 contributors that had at least one commit to the code repository of the API and its documentation, respectively. These properties satisfy R1 AND R2, our requirements for using a representative API. By selecting an open-source project we are able to access the source-code to inspect the implementation and documentation technique of the WordPress REST API. The API implements a self-documenting feature where API developers expose API endpoints over HTTP OPTIONS verb to explain the API elements. To implement this feature, the API developers describe the API elements in the code. For example:

@@

\begin{figure}
  \begin{center}
    \fbox{\includegraphics[width=\linewidth,keepaspectratio]{schema.png}}
  \end{center}
  \caption{Screenshot of documentation for Post/date}
  \label{fig:schema}
\end{figure}

@@

\bibliographystyle{IEEEtran}
\bibliography{controlled_study/IEEEabrv,controlled_study/refs}

>>>>

%\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
%\def\ps@IEEEtitlepagestyle{%
  %\def\@oddfoot{\mycopyrightnotice}%
  %\def\@evenfoot{}%
%}
%\def\mycopyrightnotice{%
  %{\footnotesize 978-1-5386-0443-4/17/\$31.00 ©2017 IEEE\hfill}% <--- Change here
  %\gdef\mycopyrightnotice{}% just in case
%}
%\begin{document}
%\title{A Study of the Effectiveness of Usage Examples in REST API Documentation}
\chapter{A Study of the Effectiveness of Usage Examples in REST API Documentation}
\label{chapter:controlled_study}

@@

Starting January 2017, the WordPress REST API V2 is no longer required to be installed as a separate plug-in since it is bundled with WordPress installation. According to the code repository, there are a total of 99 and 46 contributors that had at least one commit to the code repository of the API and its documentation, respectively. These properties satisfy R1 and R2, our requirements for using a representative API. By selecting an open-source project we are able to access the source-code to inspect the implementation and documentation technique of the WordPress REST API. The API implements a self-documenting feature where API developers expose API endpoints over HTTP OPTIONS verb to explain the API elements. To implement this feature, the API developers describe the API elements in the code. For example:

@@

\begin{figure}
  \begin{center}
    \fbox{\includegraphics[width=\linewidth,keepaspectratio]{schema.png}}
  \end{center}
  \caption{Screenshot of Documentation for Post/date}
  \label{fig:schema}
\end{figure}

@@

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,controlled_study/refs}
